Implicit yaddayadda

### 2011-10-28 papers/PLDI2012/implicitization.tex
Remarque sur widening pas monotone
nouveaux résultats de DIS

@@

\begin{table*}
\begin{center}
\setlength{\tabcolsep}{1ex}
\begin{tabular}{|l
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}|} \hline
\multicolumn{1}{|c|}{\textbf{Benchmark}}
& \multicolumn{3}{c|}{\textbf{G/S}}
& \multicolumn{3}{c|}{\textbf{PF/S}}
& \multicolumn{3}{c|}{\textbf{PF/G}}
& \multicolumn{3}{c|}{\textbf{G+PF/PF}}
& \multicolumn{3}{c|}{\textbf{G+PF/G}} \\ %\cline{2-16}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.} \\
 \hline
 \input{table1}
\end{tabular}
\end{center}
\caption{Result of the comparison of the various techniques described in this
paper: classic Abstract Interpretation (S), \emph{Guided Static Analysis} (G),
\emph{Path-focusing} (PF), and our combined technique (G+PF). For
instance, \textbf{G/S} compares the benefits of \emph{Guided Static Analysis}
over the classic Abstract interpretation algorithm.
The $\subsetneq$ column gives the percentage of invariants more precise (smaller with respect to inclusion) with the left-side technique,
$\supsetneq$ the percentage of invariants better with the right-side technique,
and ``unc.'' gives the percentage of invariants that are uncomparable, i.e
neither greater nor smaller;
the code points where both invariants are equal make up the remaining percentage.}
\label{tab:techniques}
\end{table*}

@@

Let us briefly comment the results given in more details in Table~\ref{tab:techniques} and Figure~\ref{fig:techniques}.
\emph{Guided Static Analysis} from \citet{DBLP:conf/sas/GopanR07} improves the
result of the classical Abstract Interpretation in $2.37\%$ of the control points
in $P_R$.
\emph{Path-focusing} from \citet{Monniaux_Gonnord_SAS11} gives
statistically better results, and finds better invariants than \emph{Guided
Static Analysis} in $7.28\%$ of the cases. However, it also loses precision in an
important number ($2.93\%$) of control points.
Finally, our combined technique gives the most promising results, since it is
statistically more precise than the other techniques.

The analysis using disjunctive invariants seems not to be as efficient as
expected, and often finds greater invariants than the combined technique
($11.64\%$). It probably means that our heuristic for the construction of
$\sigma$ is not effective enough. Usually, disjunctive invariants computation
finds precise loop invariants because they allow to distinguish for
instance the first loop iterations. In our case, such benefits are not
visible, since we have already unrolled every loops once.

>>>>

\MM{Peut-être dire quelque part vers ici que le widening n'est en
  général pas monotone, et que donc on ne peut jamais rien dire en
  théorie sur la précision vu qu'être plus précis à une itération peut
  faire perdre en précision la suivante ...}

@@

\begin{table*}
\begin{center}
\setlength{\tabcolsep}{1ex}
\begin{tabular}{|l
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}|} \hline
\multicolumn{1}{|c|}{\textbf{Benchmark}}
& \multicolumn{3}{c|}{\textbf{G/S}}
& \multicolumn{3}{c|}{\textbf{PF/S}}
& \multicolumn{3}{c|}{\textbf{PF/G}}
& \multicolumn{3}{c|}{\textbf{G+PF/PF}}
& \multicolumn{3}{c|}{\textbf{G+PF/G}}
& \multicolumn{3}{c|}{\textbf{DIS/G+PF}} \\ %\cline{2-16}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.} \\
 \hline
 \input{table1}
\end{tabular}
\end{center}
\caption{Result of the comparison of the various techniques described in this
paper: classic Abstract Interpretation (S), \emph{Guided Static Analysis} (G),
\emph{Path-focusing} (PF), and our combined technique (G+PF). For
instance, \textbf{G/S} compares the benefits of \emph{Guided Static Analysis}
over the classic Abstract interpretation algorithm.
The $\subsetneq$ column gives the percentage of invariants more precise (smaller with respect to inclusion) with the left-side technique,
$\supsetneq$ the percentage of invariants better with the right-side technique,
and ``unc.'' gives the percentage of invariants that are uncomparable, i.e
neither greater nor smaller;
the code points where both invariants are equal make up the remaining percentage.}
\label{tab:techniques}
\end{table*}

@@

Let us briefly comment the results given in more details in Table~\ref{tab:techniques} and Figure~\ref{fig:techniques}.
\emph{Guided Static Analysis} from \citet{DBLP:conf/sas/GopanR07} improves the
result of the classical Abstract Interpretation in $2.33\%$ of the control points
in $P_R$.
\emph{Path-focusing} from \citet{Monniaux_Gonnord_SAS11} gives
statistically better results, and finds better invariants than \emph{Guided
Static Analysis} in $8.58\%$ of the cases. However, it also loses precision in an
important number ($2.87\%$) of control points.
Finally, our combined technique gives the most promising results, since it is
statistically more precise than the other techniques.

\JH{Paragraphe a reecrire:}
The analysis using disjunctive invariants seems not to be as efficient as
expected, and often finds greater invariants than the combined technique
($11.64\%$). It probably means that our heuristic for the construction of
$\sigma$ is not effective enough. Usually, disjunctive invariants computation
finds precise loop invariants because they allow to distinguish for
instance the first loop iterations. In our case, such benefits are not
visible, since we have already unrolled every loops once.
